---
title: "The Quality of Life in North and South America"
author: "Trisha, Daphni, Aradhana"
date: "11/14/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## What is this file for?

* This file will eventually become your project report for **P02: Exploratory Data Analysis**. Specifically, you will write rmarkdown to report your exploratory data analysis.

* Please see Canvas for more details.

## ACCESSING THE /source DIRECTORY
### Example 1: Source some code and run a function
```{r}
# Example 1: Note relative path, which can be read: Up one
# directory(..), down into source (/source), and 
# then "source" an R file (data_access.R)
source("../source/data_access.R")
data_access_test()
```

### Example 2: Initialize a variable and then use it
```{r}
# Example 1: This function was "sourced" above
msg <- data_access_test(" Morgan!")
```

> `r msg` Hope you have a good day!! 

## About our charts: 



```
This bar graph depicts the crime and safety of countries in North and South America. The lower the crime rate, the higher safety a country has. The X axis is the crime index which shows the value of how much crime occured in each of the 17 countries. The Y is our dependent variable and represents the different countries in the South and North Amereica regions.The key on the right represents the safety index where it shows countries that are safest on the range from 20 to 50 above. The lighter the color, the more safer it is to live in.


Our map illustrates how easy it is to  access  healthcare in North and South America. The darker the region the harder it is for people to get heathcare and the lighter indicates easier acesability. 

This scatterplot indicates where each country stands within their cost of living index and their grocery index. A grocery index is an estimation of grocery prices in a given location compared to New York City. The cost of living index is the minimum amount of money it takes to live in that area. Some insights wee are able to see is that there is an upward trend within the countries cost of living and they are all rising consistently. With higher prices for groceries and higher cost of living it is harder for citizens to sustain in that country. 
```

## Charts

You can also embed plots, for example:

```

#bar graph 1

final_dataset <- read.csv("https://raw.githubusercontent.com/info201a-au2022/project-group-3-section-ae/main/data/New_final_dataset%20-%20Sheet1.csv")
View(final_dataset)

library(dplyr)
library(ggplot2)

df_crime <- select(final_dataset, 1,4,5)
View(df_crime)

my_bar_graph <- ggplot(df_crime, aes(x = Crime.Index, y = Country, fill = Safety.Index)) +
  geom_col() 
my_bar_graph + labs(title = "Crime and Safety in North & South America") +
  theme(plot.title = element_text(face="bold", size=15)) 
  
  
# map 2


library(ggplot2)
library(dplyr)
data <- read.csv("https://raw.githubusercontent.com/info201a-au2022/project-group-3-section-ae/main/data/New_final_dataset%20-%20Sheet1.csv")

world_coordinates <- map_data("world")

world_coordinates <- rename(world_coordinates, Country = region)

data <- inner_join(x = data, y = world_coordinates, by = "Country")


countryPlot <- ggplot()+geom_polygon(data=data,aes(x=long, y=lat, group = group, fill=Health.Care.Index))+coord_map()



#scatterplot 3

library(dplyr)

library(ggplot2)

cost_of_living <- read.csv("https://raw.githubusercontent.com/info201a-au2022/project-group-3-section-ae/main/data/New_final_dataset%20-%20Sheet1.csv")
View(cost_of_living)

df_cost_of_living <- select (final_dataset, 1,6,9)
View(df_cost_of_living)


scatterplot <- ggplot(data=df_cost_of_living, aes(x=Groceries.Index, y=Cost.of.Living.Index))+
  geom_point()

scatterplot + labs(title = "                                Cost of Food in North and South America")




```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
